\addcontentsline{toc}{chapter}{Bibliographie}
\begin{thebibliography}{99}

  \bibitem[1]{Lepers2014} Baptiste Lepers, Phd. Thesis (2014).
    \newblock \textit{Improving performances on NUMA systems architecture.}
  
  \bibitem[2]{Holistic2013} Mohammad Dashti, Alexandra Fedorova, Justin Funston,
    Fabien Gaud, Renaud Lachaize, Baptiste Lepers, Vivien Quéma, and Mark
    Roth.
    \newblock \textit{Traffic Managment: A holistic Approach to Memory
      Placement on NUMA Systems}.
    \newblock Architectural Support for Programming Languages and Operating
    Systems (ASPLOS), Houston, USA, March 2013.

  \bibitem[3]{BKDG10th} 2005–2013 Advanced Micro Devices, Inc.
  	\newblock \textit{BIOS and Kernel Developer’s Guide (BKDG) For AMD Family 10h Processors}
  	Rev 3.62  - January 11, 2013

  \bibitem[4]{CacheHierarchy}Pat Conway, Nathan Kalyanasundharam, Gregg Donley, Kevin Lepak, Bill Hughes, Advanced Micro Devices, Inc.
  	\newblock{CACHE HIERARCHY AND MEMORY SUBSYSTEM OF THE AMD OPTERON PROCESSOR}

  \bibitem[5]{BasicPerformanceMesurements}Paul J. Drongowski
  	\newblock \textit{Basic Performance Measurements for AMD AthlonTM 64, AMD OpteronTM and AMD PhenomTM Processors}
  	Advanced Micro Devices, Inc. Boston Design Center, 25 September 2008

  \bibitem[6]{AMD_dev_2}Official developper's team, Advanced Micro Devices, Inc.
  	\newblock{AMD64 Architecture Programmer’s Manual Volume 2: System Programming}

  \bibitem[7]{PMC_issues}Vincent M. Weaver, Dan Terpstra, Shirley Moore
	\newblock{Non determinism and Overcount on Mordern Performance Counter Implementations}

  


\end{thebibliography}
